\textbf{A Serious Game for Aiding the Screening of Dyslexia in Children and Young Adults}

### 2014-06-25 article.tex
Initial Proof of Serious Games for Dyslexia

\subsection{Serious Games for Dyslexia}
Previously, Section \ref{sec:dyslexia} discussed common skills and deficits associated with dyslexia, with a focus on tasks which involve minimal reading, writing and spelling. This has been done in order to allow a dyslexia screening game to be created which is as appealing and accessible as possible to those who struggle with these vital skills. It is unlikely that individuals with these difficulties will engage with a game which so openly points out their known weaknesses, instead the game content must be designed such that the link with dyslexia is as subtle as possible. In addition to this, because the game will not rely  heavily upon the players English language skills, it may easily port to other languages.

>>>>

\subsection{Serious Games for Dyslexia}
Previously, Section \ref{sec:dyslexia} discussed common skills and deficits associated with dyslexia, with a focus on tasks which involve minimal reading, writing, and spelling. This has been done in order to allow a dyslexia screening game to be created which is as appealing and accessible as possible to those who struggle with these vital skills. It is unlikely that individuals with these difficulties will engage with a game which so openly points out their known weaknesses, instead the game content must be designed such that the link with dyslexia is as subtle as possible. In addition to this, because the game will not rely  heavily upon the players English language skills, it may easily port to other languages.
